Trending assessment for nowcasts, measurements, and forecasts

### 2024-03-07 sections/01-introduction.tex
Update on Overleaf.

Nowcasting methods are now widely used in other fields, such as economics and medicine, and focus on predictions for the present, the immediate future, and the recent past (\cite{banbura2013now, bok2018macroeconomic, wolffram2023collaborative}).
Nowcasting has its origins in meteorology, and the methods were originally developed to describe the current state of the weather in detail and to predict the expected change on a time scale of a few hours (\cite{browning1989nowcasting,schmid2019nowcasting}).

>>>>

In contrast to conventional forecasting methodsNowcasting methods are now widely used in other fields, such as economics and medicine, and focus on predictions for the present, the immediate future, and the recent past (\cite{banbura2013now, bok2018macroeconomic, wolffram2023collaborative}).
Nowcasting has its origins in meteorology, and the methods were originally developed to describe the current state of the weather in detail and to predict the expected change on a time scale of a few hours (\cite{browning1989nowcasting,schmid2019nowcasting}).
